Predicting which anime are animazing through quantitative analysis

### 2024-04-18 paper/paper.qmd
Linted and styled scripts

# Introduction (longer)

@@

1.  There exists a positive relationship between rank and popularity.
2.  Except for the oldest anime, anime is popular regardless of age.
3.  The fraction of people that score an anime to the total members of an anime is a strong indicatowwwwwwwwwr of rating.

@@

Link to datasheet in repo here

>>>>

# Introduction

@@

1.  There exists a positive relationship between rank and popularity.
2.  Except for the oldest anime, anime is popular regardless of age.
3.  The fraction of people that score an anime to the total members of an anime is a strong indicator of rating.

@@

The datasheet can be found in the repo at [other/datasheet/datasheet.pdf](../other/datasheet/datasheet.pdf)
